Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-10 acl.2016/acl2016.tex
acl paper

There are a number of open-source SMT projects, most includes a decoder. The most well known is Moses, which supports phrase-based models, hierarchical phrase-based as well as various syntax-based models. Joshua also supports hiearchical and syntax models and has recently supported phrase-based models. Phrasal supports a number of variants of the phrase-based model. CDEC supports hierarchical and syntactic models.

>>>>

There are a number of open-source SMT projects, most includes a decoder. The most well known is Moses~\cite{koehn-EtAl:2007:PosterDemo}, which supports phrase-based models, hierarchical phrase-based as well as various syntax-based models. Joshua~\cite{Joshua-Decoder} also supports hiearchical and syntax models and has recently supported phrase-based models. Phrasal supports a number of variants of the phrase-based model. CDEC~\cite{dyer2010cdec} supports hierarchical and syntactic models.
